Discovering Robustness Threats by Mining the Exception Stack Traces of over 600 Android Projects

### 2014-09-03 android-stacks.tex
addressing comments. introduction

Therefore, techniques for error detection and handling are not  an optional add-on but a 
fundamental part of such apps.
% as any other modern system~\cite{bruntink2006discovering}. 
The Android platform uses the exception handling mechanism embedded
 in Java to deal with such conditions. Although the exception handling mechanism
~\cite{goodenough1975exception} is one of the most used schemes for
detecting and recovering from such exceptional conditions, studies (e.g.~\cite{miller1997issues,Robil00,shah2010understanding, garcia2007extracting,garcia2001comparative,cabral2007exception,coelho2011unveiling}),
have shown that it is generally poorly understood and the less tested parts of the system ~\cite{coelho2011unveiling}.
As a consequence that the exception-related code may become itself a source of faults, 
and may affect the system the other way around, making the system even less robust ~\cite{robillard2003static,coelho2011unveiling}.

@@

Our conjecture is that several Android applications may be suffering from similar 
fragilities on the exception-related code (of the applications themselves or 
the underlaying platform), and that such fragilities may be leading to
decrease the application robustness, leading for instance to the Uncaught Exception problem -
 which is one of the main causes of application crashes ~\cite{jo2004uncaught, zhang2012amplifying}.

@@

In Java, when an application fails due to an uncaught exception, 
it automatically terminates, while the system prints a stack trace to the console, 
or log file ~\cite{gosling2000java}.  A typical Java stack trace consists of an ordered list of 
methods that were active on the call stack before the exception has occurred,  
 and the fully qualified name of such exception.

Until recent years, the availability of issues reporting abnormal
computation states (e.g., exception stack traces) was scarce. The
available data comprised only few large scale projects (e.g. the Mozilla
crash report dataset\footnote{https://code.google.com/p/promisedata/issues/detail?id=88}).
Recently we have observed a rapid increase in the number of open
source projects that make their control version as well as the issue tracking systems
publicly available in repository hosting sites such as GitHub and Google Code.

@@

%Stack traces are a useful source of information about system crashes, and is often used to support developers in debugging~\cite{schroter2010stack}. Moreover, information %from stack traces combined with crash and bug reports can be used to support bug classification and clustering~\cite{wang2013improving, kim2011crash, %dhaliwal2011classifying}, fault-proneness prediction models~\cite{kim2013predicting} and even automated bug fixing~\cite{sinha2009fault} tools.

When available, exception stack traces provides a useful source of information about system crashes ~\cite{bettenburg2008makes} which 
 can enable different kinds of post-mortem analysis to support:  debugging~\cite{schroter2010stack}, 
 bug classification and clustering ~\cite{wang2013improving, kim2011crash, dhaliwal2011classifying},  
automated bug fixing ~\cite{sinha2009fault} and fault-proneness prediction models ~\cite{kim2013predicting}.

@@

\noindent\emph{Construct Validity} Parts of our analysis are based on the availability of stack traces on issues on
Github. In using this dataset, we make an underlying assumption: the
stack traces reported on issues are representative of real crashes in
the applications. The assumption is impossible to mitigate without access to
the full set of crash data per application. Services exist to collect all
crash data from applications, so access to such a dataset will allow for
a thorough replication of our analysis, perhaps at the individual application
level.

>>>>

Therefore, techniques for error detection and handling are not  an optional add-on but a 
fundamental part of such apps.
% as any other modern system~\cite{bruntink2006discovering}. 
The Android platform uses the exception handling mechanism embedded
 in Java to deal with such conditions. Although the exception handling mechanism
~\cite{goodenough1975exception} is one of the most used schemes for
detecting and recovering from such exceptional conditions, studies (e.g.~\cite{miller1997issues,Robil00,shah2010understanding, garcia2007extracting,garcia2001comparative,cabral2007exception,coelho2011unveiling}),
have shown that it is generally poorly understood and the less tested parts of the system ~\cite{coelho2011unveiling}.
As a consequence they may affect the system the other way around.
The exception-related code may favor the introduction of failures such as uncaught exceptions ~\cite{jo2004uncaught, zhang2012amplifying}
and unintended handler actions ~/cite{miller1997issues} (i.e., exceptions being mistakenly caught by existing handlers) 
which make the system even less robust.

@@

Our conjecture is that several Android applications may be suffering from common 
fragilities on the exception-related code (of the applications themselves or 
the underlaying platform) which may be degratind the robustness of such applications.
We call ``fragilities" characteristics on the exception-related code that favor the introduction
of aforementioned failures.

%, and that such fragilities may be leading to
%decrease the application robustness, leading for instance to the Uncaught Exception problem -
% which is one of the main causes of application crashes ~\cite{jo2004uncaught, zhang2012amplifying}.
%investigate the whether the exception stack traces
% can reveal common characteristics on the exception-related code that
%may be favoring the introduction of the aforementioned failures, which would be responsible for 
%decreasing the application robustness. We call such characteristics ``fragilities" of the exception-related code.

@@

In Java, when an application fails due to an uncaught exception, 
it automatically terminates, while the system prints a stack trace to the console, 
or log file ~\cite{gosling2000java}.  A typical Java stack trace consists of  the fully qualified name 
the thrown exception and the ordered list of methods that were active on the call stack before 
such exception has occurred.

@@

%Stack traces are a useful source of information about system crashes, and is often used to support developers in debugging~\cite{schroter2010stack}. Moreover, information %from stack traces 
%combined with crash and bug reports can be used to support bug classification and clustering~\cite{wang2013improving, kim2011crash, %dhaliwal2011classifying}, fault-proneness prediction %models~\cite{kim2013predicting} and even automated bug fixing~\cite{sinha2009fault} tools.

Until recent years, the availability of data reporting such failures was scarce. It comprised only few large scale projects (e.g. the Mozilla
crash report dataset\footnote{https://code.google.com/p/promisedata/issues/detail?id=88}).
Recently we have observed a rapid increase in the number of open
source projects that make their version control systems as well as the issue tracking systems
publicly available in repository hosting sites such as GitHub and Google Code.

When available, the exception stack traces provide a useful source of information about system crashes ~\cite{bettenburg2008makes} which 
 can enable different kinds of post-mortem analysis and support:  debugging~\cite{schroter2010stack}, 
 bug classification and clustering ~\cite{wang2013improving, kim2011crash, dhaliwal2011classifying},  
automated bug fixing ~\cite{sinha2009fault} and fault-proneness prediction models ~\cite{kim2013predicting}.

@@

\noindent\emph{Construct Validity} Parts of our analysis are based on the availability of stack traces on issues on
Github. In using this dataset, we make an underlying assumption: the
stack traces reported on issues are representative of real crashes in
the applications. The assumption is impossible to mitigate without access to
the full set of crash data per application. Some services exist to collect 
crash data from mobile applications ~\cite{BugSe14,BugSn14,Googl14,Acra14}.
However, such services do not provide open access to the crash reports
of their client applications. Having access to such a dataset would allow 
a replication of our analysis on an even wider setting.
